Check matrix correlations

### 2018-06-11 Analysis/04-CheckMatrixCorrelation.Rmd
Proportion replacement

```{r}
## Getting the proportion of replaced characters
get.proportion.replace <- function(matrix, path) {
    ## Getting one matrix in a comparable format
    get.one.matrix <- function(path, matrix, type) {
        return(unlist(apply(do.call(rbind, read.nexus.data(paste0(path, matrix, "_", type, ".nex"))), 2, list), recursive = FALSE))
    }

@@

```{r, fig.height = 6, fig.width = }

boxplot(results_rand[[3]], xaxis = "n")

plot.results.single <- function(taxa_list, metric, what, ylim, legend = FALSE, NTS = TRUE, ylab, xlab, axislab, ...) {

    ## Graphic parameters
    ## Colours
    cols <- c("red", "orange", "green3", "lightgreen", "blue", "lightblue")

    ## Y lab
    if(missing(ylab)) {
        if(metric == 1) ylab <- "Similarity (Matching Cluster)"
        if(metric == 2) ylab <- "Similarity (Robinson-Foulds)"
        if(metric == 3) ylab <- "Similarity (Nodal Split)"
        if(metric == 4) ylab <- "Similarity (Triplets)"
    }

    ## Y lim
    get.min.list <- function(X, metric) {
        return(min(unlist(X[,metric])))
    }

    min <- min(unlist(lapply(unlist(unlist(unlist(taxa_list, recursive = FALSE), recursive = FALSE), recursive = FALSE), get.min.list, metric)))
    if(min < 0) {
        ylim <- c(min,1)
    } else {
        ylim <- c(0,1)
    }

    ## X lab
    if(missing(xlab)) {
        xlab <- "Characters"
    }

    ## axis lab
    if(missing(axislab)) {
        axislab <- c("100", "350", "1000")
    }

    ## Horizontal line
    line <- 0

    if(what == "null") {
        boxplot(xlab = xlab, ylab = ylab, xaxt = "n", ylim = ylim, col = rep(cols, 3), las = 1, ...,
            ## c100
            unlist(taxa_list$c100$bayesian$rand$maxi[,metric]), unlist(taxa_list$c100$parsimony$rand$maxi[,metric]),
            unlist(taxa_list$c100$bayesian$rand$mini[,metric]), unlist(taxa_list$c100$parsimony$rand$mini[,metric]),
            unlist(taxa_list$c100$bayesian$rand$norm[,metric]), unlist(taxa_list$c100$parsimony$rand$norm[,metric]),
            ## c350
            unlist(taxa_list$c350$bayesian$rand$maxi[,metric]), unlist(taxa_list$c350$parsimony$rand$maxi[,metric]),
            unlist(taxa_list$c350$bayesian$rand$mini[,metric]), unlist(taxa_list$c350$parsimony$rand$mini[,metric]),
            unlist(taxa_list$c350$bayesian$rand$norm[,metric]), unlist(taxa_list$c350$parsimony$rand$norm[,metric]),
            ## c1000
            unlist(taxa_list$c1000$bayesian$rand$maxi[,metric]), unlist(taxa_list$c1000$parsimony$rand$maxi[,metric]),
            unlist(taxa_list$c1000$bayesian$rand$mini[,metric]), unlist(taxa_list$c1000$parsimony$rand$mini[,metric]),
            unlist(taxa_list$c1000$bayesian$rand$norm[,metric]), unlist(taxa_list$c1000$parsimony$rand$norm[,metric])
            )

        ## X axis
        axis(1, 1:18, labels = FALSE, tick = FALSE)
        axis(1, c(3.5, 9.5, 15.5), tick = FALSE, labels = axislab)
        ## Lines
        abline(v = 6.5) ; abline(v = 12.5)
        abline(h = line, col = "grey", lty = 2)
        ## Legend
        if(legend) {
            legend("bottomleft", col = cols, pch = 19, bty = "n", title = "Character differences:", cex = 0.8,
                legend = c("Maximised (Bayesian)", "Maximised (Parsimony)",
                           "Minimised (Bayesian)", "Minimised (Parsimony)",
                           "Normal (Bayesian)", "Normal (Parsimony)")
                )
        }
    }

    if(what == "best") {
        boxplot(xlab = xlab, ylab = ylab, xaxt = "n", ylim = ylim, col = rep(cols, 3), las = 1, ...,
            ## c100
            unlist(taxa_list$c100$bayesian$norm$maxi[,metric]), unlist(taxa_list$c100$parsimony$norm$maxi[,metric]),
            unlist(taxa_list$c100$bayesian$norm$mini[,metric]), unlist(taxa_list$c100$parsimony$norm$mini[,metric]),
            unlist(taxa_list$c100$bayesian$norm$rand[,metric]), unlist(taxa_list$c100$parsimony$norm$rand[,metric]),
            ## c350
            unlist(taxa_list$c350$bayesian$norm$maxi[,metric]), unlist(taxa_list$c350$parsimony$norm$maxi[,metric]),
            unlist(taxa_list$c350$bayesian$norm$mini[,metric]), unlist(taxa_list$c350$parsimony$norm$mini[,metric]),
            unlist(taxa_list$c350$bayesian$norm$rand[,metric]), unlist(taxa_list$c350$parsimony$norm$rand[,metric]),
            ## c1000
            unlist(taxa_list$c1000$bayesian$norm$maxi[,metric]), unlist(taxa_list$c1000$parsimony$norm$maxi[,metric]),
            unlist(taxa_list$c1000$bayesian$norm$mini[,metric]), unlist(taxa_list$c1000$parsimony$norm$mini[,metric]),
            unlist(taxa_list$c1000$bayesian$norm$rand[,metric]), unlist(taxa_list$c1000$parsimony$norm$rand[,metric])
            )

        ## X axis
        axis(1, 1:18, labels = FALSE, tick = FALSE)
        axis(1, c(3.5, 9.5, 15.5), tick = FALSE, labels = axislab)
        ## Lines
        abline(v = 6.5) ; abline(v = 12.5)
        abline(h = line, col = "grey", lty = 2)
        ## Legend
        if(legend) {
            legend("bottomleft", col = cols, pch = 19, bty = "n", title = "Character differences:", cex = 0.8,
                legend = c("Maximised (Bayesian)", "Maximised (Parsimony)",
                           "Minimised (Bayesian)", "Minimised (Parsimony)",
                           "Randomised (Bayesian)", "Randomised (Parsimony)")
                )
        }
    }

    if(what == "true") {
        boxplot(xlab = xlab, ylab = ylab, xaxt = "n", ylim = ylim, col = rep(cols[1:4], 3), las = 1, ...,
            ## c100
            unlist(taxa_list$c100$bayesian$norm$true[,metric]), unlist(taxa_list$c100$parsimony$norm$true[,metric]),
            unlist(taxa_list$c100$bayesian$rand$true[,metric]), unlist(taxa_list$c100$parsimony$rand$true[,metric]),
            ## c350
            unlist(taxa_list$c350$bayesian$norm$true[,metric]), unlist(taxa_list$c350$parsimony$norm$true[,metric]),
            unlist(taxa_list$c350$bayesian$rand$true[,metric]), unlist(taxa_list$c350$parsimony$rand$true[,metric]),
            ## c1000
            unlist(taxa_list$c1000$bayesian$norm$true[,metric]), unlist(taxa_list$c1000$parsimony$norm$true[,metric]),
            unlist(taxa_list$c1000$bayesian$rand$true[,metric]), unlist(taxa_list$c1000$parsimony$rand$true[,metric])
            )

        ## X axis
        axis(1, 1:12, labels = FALSE, tick = FALSE)
        axis(1, c(2.5, 6.5, 10.5), tick = FALSE, labels = axislab)
        ## Lines
        abline(v = 4.5) ; abline(v = 8.5)
        abline(h = line, col = "grey", lty = 2)
        ## Legend
        if(legend) {
            legend("bottomleft", col = cols[1:4], pch = 19, bty = "n", title = "Character differences:", cex = 0.8,
                legend = c("Normal (Bayesian)", "Normal (Parsimony)",
                           "Randomised (Bayesian)", "Randomised (Parsimony)")
                )
        }
    }

    if(what == "check") {
        boxplot(xlab = xlab, ylab = ylab, xaxt = "n", ylim = ylim, col = rep(cols[1:4], 3), las = 1, ...,
            ## c100
            unlist(taxa_list$c100$bayesian$norm$rand[,metric]), unlist(taxa_list$c100$parsimony$norm$rand[,metric]),
            unlist(taxa_list$c100$bayesian$rand$norm[,metric]), unlist(taxa_list$c100$parsimony$rand$norm[,metric]),
            ## c350
            unlist(taxa_list$c350$bayesian$norm$rand[,metric]), unlist(taxa_list$c350$parsimony$norm$rand[,metric]),
            unlist(taxa_list$c350$bayesian$rand$norm[,metric]), unlist(taxa_list$c350$parsimony$rand$norm[,metric]),
            ## c1000
            unlist(taxa_list$c1000$bayesian$norm$rand[,metric]), unlist(taxa_list$c1000$parsimony$norm$rand[,metric]),
            unlist(taxa_list$c1000$bayesian$rand$norm[,metric]), unlist(taxa_list$c1000$parsimony$rand$norm[,metric])
            )

        ## X axis
        axis(1, 1:12, labels = FALSE, tick = FALSE)
        axis(1, c(2.5, 6.5, 10.5), tick = FALSE, labels = axislab)
        ## Lines
        abline(v = 4.5) ; abline(v = 8.5)
        abline(h = line, col = "grey", lty = 2)
        ## Legend
        if(legend) {
            legend("bottomleft", col = cols[1:4], pch = 19, bty = "n", title = "Character differences:", cex = 0.8,
                legend = c("Normal (Bayesian)", "Normal (Parsimony)",
                           "Randomised (Bayesian)", "Randomised (Parsimony)")
                )
        }
    }
}

combine_results <- unlist(lapply(replacements[[1]][[1]], function(X) return(X[[1]])))

>>>>

```{r}
## Getting the proportion of replaced characters
get.proportion.replace <- function(matrix, path) {
    ## Getting one matrix in a comparable format
    get.one.matrix <- function(path, matrix, type) {
        return(unlist(apply(do.call(rbind,
                                    read.nexus.data(paste0(path, matrix, "_", type, ".nex"))
                            ), 2, list), recursive = FALSE))
    }

@@

```{r, fig.height = 18, fig.width = 6}
## Plotting the different proportion results
plot.proportions <- function(data, ...) {
    ## Default colours
    cols <- gray.colors(3)
    ## Boxes
    boxplot(xlab = "", ylab = "Proportion of replacement", xaxt = "n", ylim = c(0, 1), col = cols,
            c(data[[1]], data[[2]], data[[3]]), ...)
    legend("topleft", legend = names(data), pch = 19, col = cols, bty = "n")
    ## X axis
    axis(1, 1:9, labels = FALSE, tick = FALSE)
    axis(1, c(2, 5, 8), tick = FALSE, labels = names(data))
    ## Lines
    abline(v = 3.5) ; abline(v = 6.5)
}

par(mfrow = c(3,1))
plot.proportions(results_maxi, main = "Maximised differences")
plot.proportions(results_mini, main = "Minimised differences")
plot.proportions(results_rand, main = "Randomised differences")

```
